Maximizing Ink in Symmetric Partial Edge Drawings of $k$-plane Graphs

### 2018-01-04 eurocg/paper.tex
minor
...

% Author metadata::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Maximizing Ink in Symmetric Partial Edge Drawings of $k$-plane Graphs}
%{Maximal Symmetric Partial Edge Drawings With Degree $ > 2$}
%optional, in case that the title is too long; 
%the running title should fit into the top page column
\titlerunning{MaxSPEDs with degree $ > 2$}

@@

\section{Hardness}
\fabian{Use the reduction from Till Bruckdorfers Dissertation \cite{b-sgh-15}. The Clauses can be modelled as triangles, the Variables as Circles with every second segment connected to a path. Path should have even length, segments are of length four.}

@@

\section{Two Polynomial Cases}

@@

	Let $ u \in V $ be not a leaf, but for all children $ v \in c(u) $ we know the values $ \solshort(v) $ and $ \sollong(v) $ for every stub length $ \ell_i(v) $. By Lemma~\ref{lem:compute_vertex} we can compute $ \sollong(u) $ and $ \solshort(u) $ in $ O(k) $. Hence if $ r \in V $ is the root of the tree $ C $, computing $ T_i(r) $ for all $ i $ takes $ O(nk) $ time. The maximum of
\end{proof}

>>>>

% Author metadata::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Maximizing Ink in Symmetric Partial Edge Drawings of $k$-plane Graphs}
%{Maximal Symmetric Partial Edge Drawings With Degree $ > 2$}
%optional, in case that the title is too long; 
%the running title should fit into the top page column
%\titlerunning{MaxSPEDs with degree $ > 2$}

@@

\section{Hardness of \maxsped for $k\ge3$}
\fabian{Use the reduction from Till Bruckdorfers Dissertation \cite{b-sgh-15}. The Clauses can be modelled as triangles, the Variables as Circles with every second segment connected to a path. Path should have even length, segments are of length four.}

@@

\section{Two polynomial special cases}

@@

	Let $ u \in V $ be not a leaf, but for all children $ v \in c(u) $ we know the values $ \solshort(v) $ and $ \sollong(v) $ for every stub length $ \ell_i(v) $. By Lemma~\ref{lem:compute_vertex} we can compute $ \sollong(u) $ and $ \solshort(u) $ in $ O(k) $. Hence if $ r \in V $ is the root of the tree $ C $, computing $ T_i(r) $ for all $ i $ takes $ O(nk) $ time.

	It remains to show that the maximum over all $ T_i(r) $, with $ r \in V $ being the root, is the optimal value over all solutions to the \maxsped problem on $ G $. Assume $ t $ is the maximum value for some $ T_i(r) $'s and $ r $ the root. Let $ t' $ be the value of another solution on $ G $ with drawing $ \Gamma $ and $ t' > t $. 
\end{proof}
